\section{Introduction}
\subsection{Previous Work}
Wireless Sensor Networks(WSN) are being used in a variety of exciting 
applications. The UUTE project{4561146} will provide more independence 
and mobility to the elderly and recovering patients by using wearable 
wireless sensors to monitor their health. But many WSN applications 
depend on a limited battery as a source of energy.  Using power 
effectively is important in keeping the WSN functional and cost efficient.
 In{6558065},Manju identifies the activities which waste battery power 
the most in a WSN node.  A node wastes energy when the packet it sends 
becomes corrupt due to a collision, and retransmissions are required 
since error correcting codes, which use additional power, are not 
often used {4476299}. Also, overheating is when a node is needlessly 
awakened from sleep mode when it intercepts a transmission that was 
meant for a different node.  Misuse of control packet {6558065} can 
also drain power by keeping a node listening, until a timeout occurs, 
for packets that will never arrive or by causing the a node to needlessly 
transmit responses.
	

An attacker could take advantage of these power wasting scenarios and 
force them to happen more often than they normal would.  Any attacks 
that causes these effects for long periods of time are considered 
Denial-of-Sleep {4476299} attacks because a node is being forced to 
use up power to performing meaningless tasks instead of switching to 
a power-conserving sleep mode. These previously mentioned battery draining
 scenarios all occur in the MAC layer, but Vasserman and Hopper{6112758} 
bring up the point that attackers could achieve the same goal in the 
network layer by forcing the packets to take the longest path possible 
to reach its destination, or worse: route the packets in an endless loop, 
which is called a carousel attack.  Vasserman also explains that attacker 
nodes on a wireless ad-hoc network, such as a WSN, typically try to use 
as few transmissions as possible while maximizing the wasted power 
consumption of victim nodes. Instead of blasting control packets at a 
high rate, attacker nodes smartly send transmission to avoid being 
identified as malicious by nearby nodes.

\subsection{Contents}
In this paper, we will be simulating several simple wireless sensor node 
attacks in order to figure out methods of protecting against such attacks.
 First we will establish what resources and what information  
the attacker will have for each simulation. Then we will explain the 
details of the scenario we are simulating, including the type and the 
size of battery  used by the node, and the size of the packets that 
will be transmitted. We will also describe how the simulation is set up, 
as well as the assumptions we took while designing them. 
With the framework of the simulation established, we will analyze the 
patterns and implications of the collected data. Then we will use the 
data analysis to support our proposal for countermeasures against power 
consumption attacks.

\subsection{Goal}
The goal of this simulation is to gain an understanding of the 
effects of power consumption attacks on WSN nodes. We will be able 
to understand the weaknesses and limitations the sensor nodes, and 
we can use this insight to figure out mitigation techniques that 
could potentially be put into practice. Also we want to be able to 
recommend certain design choices, such as battery type, when 
manufacturing WSN nodes.

